\Title

### 2020-03-23 manuscript/manuscript.tex
Rename block median sources for block averaged sources (#37)
Standarize the source layout name to block_averaged_sources.
Improve manuscript

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
            points that resemble a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
            obtained through the \emph{sources beneath data} layout.
        (c) Location of the \SourceLayoutsSchematicsBlockaveragedSources{}
            sources obtained through the \emph{block averaged sources} layout.
        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
            obtained through the \emph{grid sources} layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

@@

\noindent where \emph{data point height} is the elevation of the corresponding
observation (or block averaged) point to the source, \emph{depth factor} and
\emph{relative depth} are parameters and \emph{mean distance} is the mean
distance to the $k$ nearest source neighbours.
This term will be smaller in case of clustered sources, making them shallower
than scattered and distant sources.

@@

Worth mention that the two last approaches (the \emph{relative depth} and the
\emph{variable depth}) could not be applied to \emph{grid sources}.

@@

Our goal is to to compare the performance of all source distributions from
Table~\ref{tab:source-distributions} when predicting harmonic field data using
the equivalent layer technique.
To do so we have created a synthetic model made out of prisms of different
shape and density contrasts.
The gravitational effect of this synthetic model have been computed on
a regular grid (\emph{target} grid) at a constant height and on two different
set of observation points that we will call \emph{synthetic surveys}: a ground
and an airborne survey.
The data from each synthetic survey is interpolated on the points of the
\emph{target} grid.
The interpolations are carried out using each source distribution and combining
different parameter values for each distribution.
Each prediction is then scored against the \emph{target} grid.
We can then quantitatively compare how accurate is each source distribution at
predicting unobserved data on each synthetic survey and quantify the
computational load needed to do it.

@@

        \multirow{11}{*}{Block averaged sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesConstantDepthDepth
                  \GroundBlockAveragedSourcesConstantDepthDepthIncrement
                & \BestGroundBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesConstantDepthSpacing
                  \GroundBlockAveragedSourcesConstantDepthSpacingIncrement
                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesConstantDepthDamping
                  \GroundBlockAveragedSourcesConstantDepthDampingIncrement
                & \BestGroundBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesRelativeDepthDepth
                  \GroundBlockAveragedSourcesRelativeDepthDepthIncrement
                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesRelativeDepthSpacing
                  \GroundBlockAveragedSourcesRelativeDepthSpacingIncrement
                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesRelativeDepthDamping
                  \GroundBlockAveragedSourcesRelativeDepthDampingIncrement
                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesVariableDepthDepth
                  \GroundBlockAveragedSourcesVariableDepthDepthIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestGroundBlockAveragedSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
                  \GroundBlockAveragedSourcesVariableDepthDepthFactorIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundBlockAveragedSourcesVariableDepthKNearest
                  \GroundBlockAveragedSourcesVariableDepthKNearestIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesVariableDepthSpacing
                  \GroundBlockAveragedSourcesVariableDepthSpacingIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesVariableDepthDamping
                  \GroundBlockAveragedSourcesVariableDepthDampingIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

@@

        \multirow{11}{*}{Block averaged sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesConstantDepthDepth
                  \AirborneBlockAveragedSourcesConstantDepthDepthIncrement
                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesConstantDepthSpacing
                  \AirborneBlockAveragedSourcesConstantDepthSpacingIncrement
                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesConstantDepthDamping
                  \AirborneBlockAveragedSourcesConstantDepthDampingIncrement
                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesRelativeDepthDepth
                  \AirborneBlockAveragedSourcesRelativeDepthDepthIncrement
                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
                  \AirborneBlockAveragedSourcesRelativeDepthSpacingIncrement
                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesRelativeDepthDamping
                  \AirborneBlockAveragedSourcesRelativeDepthDampingIncrement
                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesVariableDepthDepth
                  \AirborneBlockAveragedSourcesVariableDepthDepthIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestAirborneBlockAveragedSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
                  \AirborneBlockAveragedSourcesVariableDepthDepthFactorIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneBlockAveragedSourcesVariableDepthKNearest
                  \AirborneBlockAveragedSourcesVariableDepthKNearestIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesVariableDepthSpacing
                  \AirborneBlockAveragedSourcesVariableDepthSpacingIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesVariableDepthDamping
                  \AirborneBlockAveragedSourcesVariableDepthDampingIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

>>>>

Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
observation points that simulates a ground survey, and the possible location of
sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
averaged sources} and (d) the \emph{grid sources} layouts.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
            points that resemble a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
            obtained through the \emph{sources below data} layout.
        (c) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
            sources obtained through the \emph{block averaged sources} layout.
        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
            obtained through the \emph{grid sources} layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

@@

\noindent where \emph{data point height} is the elevation of the corresponding
observation (or block averaged) point, \emph{mean distance} is the mean
distance to the $k$ nearest source neighbours, \emph{depth factor} and
\emph{relative depth} are parameters.
The addition of this new term will make clustered sources to be shallower than
scattered and distant sources.

@@

@@

Our goal is to to compare the performance of all source distributions from
Table~\ref{tab:source-distributions} when predicting harmonic field data using
the equivalent layer technique.
To do so we have created a synthetic model made out of prisms of different
shape and density contrasts.
The gravitational effect of this synthetic model have been computed on
a regular grid (\emph{target} grid) at a constant height and on two different
set of observation points that we will call \emph{synthetic surveys}: a ground
and an airborne survey.
The data from each synthetic survey is interpolated on the points of the
\emph{target} grid and then scored against the \emph{target} grid.
We can then quantitatively compare how accurate is each source distribution at
predicting unobserved data on each synthetic survey and quantify the
computational load needed to do it.

@@

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesConstantDepthDepth
                  \GroundBlockAveragedSourcesConstantDepthDepthIncrement
                & \BestGroundBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesConstantDepthSpacing
                  \GroundBlockAveragedSourcesConstantDepthSpacingIncrement
                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesConstantDepthDamping
                  \GroundBlockAveragedSourcesConstantDepthDampingIncrement
                & \BestGroundBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesRelativeDepthDepth
                  \GroundBlockAveragedSourcesRelativeDepthDepthIncrement
                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesRelativeDepthSpacing
                  \GroundBlockAveragedSourcesRelativeDepthSpacingIncrement
                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesRelativeDepthDamping
                  \GroundBlockAveragedSourcesRelativeDepthDampingIncrement
                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesVariableDepthDepth
                  \GroundBlockAveragedSourcesVariableDepthDepthIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestGroundBlockAveragedSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
                  \GroundBlockAveragedSourcesVariableDepthDepthFactorIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundBlockAveragedSourcesVariableDepthKNearest
                  \GroundBlockAveragedSourcesVariableDepthKNearestIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesVariableDepthSpacing
                  \GroundBlockAveragedSourcesVariableDepthSpacingIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesVariableDepthDamping
                  \GroundBlockAveragedSourcesVariableDepthDampingIncrement
                & \BestGroundBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

@@

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesConstantDepthDepth
                  \AirborneBlockAveragedSourcesConstantDepthDepthIncrement
                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesConstantDepthSpacing
                  \AirborneBlockAveragedSourcesConstantDepthSpacingIncrement
                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesConstantDepthDamping
                  \AirborneBlockAveragedSourcesConstantDepthDampingIncrement
                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesRelativeDepthDepth
                  \AirborneBlockAveragedSourcesRelativeDepthDepthIncrement
                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
                  \AirborneBlockAveragedSourcesRelativeDepthSpacingIncrement
                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesRelativeDepthDamping
                  \AirborneBlockAveragedSourcesRelativeDepthDampingIncrement
                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesVariableDepthDepth
                  \AirborneBlockAveragedSourcesVariableDepthDepthIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestAirborneBlockAveragedSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
                  \AirborneBlockAveragedSourcesVariableDepthDepthFactorIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneBlockAveragedSourcesVariableDepthKNearest
                  \AirborneBlockAveragedSourcesVariableDepthKNearestIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesVariableDepthSpacing
                  \AirborneBlockAveragedSourcesVariableDepthSpacingIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesVariableDepthDamping
                  \AirborneBlockAveragedSourcesVariableDepthDampingIncrement
                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule
